\LARGE \bf Predicting Initialization Effectiveness for Trajectory Optimization

### 2014-02-13 paper.tex

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|r|r|}
\hline 
 & baseline & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin & 59.2 & 82.6	& 82.2 & 74.7 & 82.3 & 82.2 & 70.1 & 63.15 \\ \hline
gap-dubin & 56.4 & 88.6 & 87.9 & 77.3 & 86.2 & 87.1 & 76.2 & 76.0 \\ \hline
squared-dubin & 56.8 & 89.3 & 	87.1 & 	77.5 &	88.2 &	85.0 &	 61.7	& 61.5 \\ \hline \hline

bookshelf & 63.0 & 77.7 & 	77.5 &	73.9 &	77.5 &	76.3 &	68.7 & 70.0 \\ \hline
skew-bookshelf & 62.1 & 80.4 &	74.3 & 	77.9 & 	76.2 &	72.3 &	63.7 &	65.0 \\ \hline
countertop & 69 & 70.1	& 72.8 & 	74.5	 & 69.6 & 	73.9 &	77.7 &	63.6 \\ \hline
industrial & 67.2 & 78.5 &	78.2 &	78.4 &	78.2 &	76.9 &	80.2 & 	73.7 \\ \hline
industrial2 & 50.3 & 61.1 & 	62.1	 & 64.1 &	61.2 & 	62.3 & 	64.5 &	58.2 \\ \hline \hline

livingroom & 61.0 & 85.5	& 88.4 &	 83.6 &	84.7 &	87.4 & 	82.8 &	81.6 \\ \hline
livingroom2 & 53.7 & 80.3 &	 80.5	& 76.7 &	 78.6 &	77.9 & 	71.5 & 	66.6 \\ \hline
kitchen & 59.0 & 65 & 	64.2 & 	60.4 &	66.9 & 	66.2 & 	60.3 & 	73.6 \\ \hline
kitchen2 & 54.0 & 64.6 &	65.3 & 	61.6 & 	65.0 & 	65.0 & 	61.0 &	61.5 \\ \hline
hotel & 98 & 98.1 &	98.1 & 	98.2 &	98.1 &	98.1 &	97	& 98.1 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%): We compare the prediction accuracy of the baseline (i.e., the percentage of majority trajectory label) with the prediction results when using all the features we designed $\fssd+\fcon+\fsht$ and other combinations of features.}
\label{tab:result}
\end{table*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|r|r|}
\hline 
 & baseline & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin to squared-dubin &  56.8 & 49.7 & 49.0 &	74.4 & 	56.9 & 	60.3	 & 67.9	& 55.5
 \\ \hline
squared-dubin to jagged-dubin & 59.2 & 56.9 &	56.8 &	71.1 & 	56.9 &	56.9 &	61.2 &	63.8 \\ \hline
bookshelf to skew-bookshelf & 62.1 & 57.1 &	59.4 &	82.1 & 	53.2 &	57.3 &	60.3 &	67.4 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) when applying the classifier learned on one benchmark onto trajectories from other benchmarks. The baseline is the percentage of majority trajectory label of the benchmark where the classifier is transferred to.}
\label{tab:result2}
\end{table*}

>>>>

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|r|r|r|}
\hline 
 & baseline & ${\bf z}_\textrm{conv} +\fssd+\fcon+\fsht$  & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin & 59.2 & 90.2  & 82.6	& 82.2 & 74.7 & 82.3 & 82.2 & 70.1 & 63.15 \\ \hline
gap-dubin & 56.4 & 90.5 & 88.6 & 87.9 & 77.3 & 86.2 & 87.1 & 76.2 & 76.0 \\ \hline
squared-dubin & 56.8 & 98.3 & 89.3 & 	87.1 & 	77.5 &	88.2 &	85.0 &	 61.7	& 61.5 \\ \hline \hline

bookshelf & 63.0 & 100 & 77.7 & 	77.5 &	73.9 &	77.5 &	76.3 &	68.7 & 70.0 \\ \hline
skew-bookshelf & 62.1 & & 80.4 &	74.3 & 	77.9 & 	76.2 &	72.3 &	63.7 &	65.0 \\ \hline
countertop & 69 & 99.7 & 70.1	& 72.8 & 	74.5	 & 69.6 & 	73.9 &	77.7 &	63.6 \\ \hline
industrial & 67.2 & 83.8 & 78.5 &	78.2 &	78.4 &	78.2 &	76.9 &	80.2 & 	73.7 \\ \hline
industrial2 & 50.3 & 96.2 & 61.1 & 	62.1	 & 64.1 &	61.2 & 	62.3 & 	64.5 &	58.2 \\ \hline \hline

livingroom & 61.0 & & 85.5	& 88.4 &	 83.6 &	84.7 &	87.4 & 	82.8 &	81.6 \\ \hline
livingroom2 & 53.7 & & 80.3 &	 80.5	& 76.7 &	 78.6 &	77.9 & 	71.5 & 	66.6 \\ \hline
kitchen & 59.0 & & 65 & 	64.2 & 	60.4 &	66.9 & 	66.2 & 	60.3 & 	73.6 \\ \hline
kitchen2 & 54.0 & & 64.6 &	65.3 & 	61.6 & 	65.0 & 	65.0 & 	61.0 &	61.5 \\ \hline
hotel & 98 & & 98.1 &	98.1 & 	98.2 &	98.1 &	98.1 &	97	& 98.1 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%): We compare the prediction accuracy of the baseline (i.e., the percentage of majority trajectory label) with the prediction results when using all the features we designed $\fssd+\fcon+\fsht$ and other combinations of features.}
\label{tab:result}
\end{table*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|r|r|r|}
\hline 
 & baseline &  ${\bf z}_\textrm{conv} +\fssd+\fcon+\fsht$ & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin to squared-dubin &  56.8 & 88.8 & 49.7 & 49.0 &	74.4 & 	56.9 & 	60.3	 & 67.9	& 55.5
 \\ \hline
squared-dubin to jagged-dubin & 59.2 & 58.9 & 56.9 &	56.8 &	71.1 & 	56.9 &	56.9 &	61.2 &	63.8 \\ \hline
bookshelf to skew-bookshelf & 62.1 & & 57.1 &	59.4 &	82.1 & 	53.2 &	57.3 &	60.3 &	67.4 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) when applying the classifier learned on one benchmark onto trajectories from other benchmarks. The baseline is the percentage of majority trajectory label of the benchmark where the classifier is transferred to.}
\label{tab:result2}
\end{table*}
